Abstraction and Invariance for Algebraically Indexed Types

### 2012-07-04 paper/paper.tex

  Outside computer science, invariance under change is a common theme
  running through many areas mathematics and physics. For example, the
  area of a triangle is not altered by rotation or flipping. If we
  scale a triangle, then we scale its area, maintaining an invariant
  relationship between the triangle and its area. The transformations
  that properties are invariant under are often organised into groups,
  the algebraic structure reflecting the composability and
  invertibility of transformations.

>>>>

  Outside computer science, invariance under change is a common theme
  running through many areas mathematics and physics. For example, the
  area of a triangle is not altered by rotation or flipping. If we
  scale a triangle, then we scale its area, maintaining an invariant
  relationship between the triangle and its area. The transformations
  under which properties are invariant are often organised into
  groups, with the algebraic structure reflecting the composability
  and invertibility of transformations.
